Reanalysis Step 2: Multiple Imputation

### 2025-09-02 reanalysis-2-multiple_imputation.qmd
imputation fix

# ANALYSIS MODE: "test" or "final"
# test = 2 imputations, 2 iterations (fast)
# final = 30 imputations, 20 iterations (slow but thorough)
analysis_mode <- "final"  # Change to "final" for production run
log_message(paste0("Analysis mode: ", analysis_mode))

# CACHING CONFIGURATION FOR MICE
# Set to TRUE to use cached MICE results (skip imputation, only run post-processing)
use_cached_mice <- TRUE
mice_cache_file <- file.path(reanalysis_data_dir, "mice_results.rds")
log_message(paste0("MICE caching: ", ifelse(use_cached_mice, "ENABLED", "DISABLED")))

# Set parameters based on mode
if (analysis_mode == "test") {
  n_imputations <- 2
  n_iterations <- 2
} else if (analysis_mode == "final") {
  n_imputations <- 30
  n_iterations <- 20
} else {
  stop("Invalid analysis_mode. Must be 'test' or 'final'")
}

>>>>

# ANALYSIS MODE: "test" or "final"
# test = 2 imputations, 2 iterations (fast)
# final = 50 imputations, 20 iterations (slow but thorough)
analysis_mode <- "final"  # Change to "final" for production run
log_message(paste0("Analysis mode: ", analysis_mode))

# CACHING CONFIGURATION FOR MICE
# Set to TRUE to use cached MICE results (skip imputation, only run post-processing)
use_cached_mice <- FALSE
mice_cache_file <- file.path(reanalysis_data_dir, "mice_results.rds")
log_message(paste0("MICE caching: ", ifelse(use_cached_mice, "ENABLED", "DISABLED")))

# Set parameters based on mode
if (analysis_mode == "test") {
  n_imputations <- 2
  n_iterations <- 2
} else if (analysis_mode == "final") {
  n_imputations <- 50
  n_iterations <- 20
} else {
  stop("Invalid analysis_mode. Must be 'test' or 'final'")
}
